Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-05-27 main_new.tex
updates

\begin{figure}[!h] 
  \centering 
  \subfigure[Modern ocean sensing network, where robotic assets augment
  ship based measurements to increase coverage of the phenomena.]{\includegraphics[width =
    0.48\textwidth]{Figures/envir.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Different important coastal processes directly or indirectly
  associated with gradients and boundaries.]{\includegraphics[width =
    0.48\textwidth]{Figures/envir_ocean.pdf}\label{fig:envir2}}
  \caption{Ocean observation is moving away from single-ship sampling
    towards more collaborative networked operations in order to resolve
    the numerous processes and their interaction.} \label{fig:envir}
\end{figure}

>>>>

\begin{figure}[!h] 
  \centering 
  \subfigure[Modern ocean sensing network, where robotic assets augment
  ship based measurements to increase coverage of the phenomena.]{\includegraphics[width =
    0.48\textwidth]{Figures/envir.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Different coastal processes directly or indirectly
  associated with gradients and boundaries.]{\includegraphics[width =
    0.48\textwidth]{Figures/envir_ocean.pdf}\label{fig:envir2}}
  \caption{Ocean observation is moving away from single-ship sampling
    towards more collaborative networked operations in order to resolve
    the numerous processes and their interaction.} \label{fig:envir}
\end{figure}
